Modal type theory based on the intuitionistic epistemic logic

### 2018-02-07 article.tex
added

Where $\mathbb{V}^{*}$ and $\Lambda_{{\bf K}}^{*}$ denote the set of finite sequences of variables $\mathbb{V}^0 \times \mathbb{V}^1 \times \dots$
and the set of finite sequences of terms $\Lambda_{{\bf K}}^0 \times \Lambda_{{\bf K}}^1 \times \dots$. Note that the sequence of variables $\vec{x}$ and the sequence of terms $\vec{M}$ should have the same length.
Otherwise, term is not well-formed.

@@

Because the local binding

@@

@@

\begin{prop} Simmetricity of local binding

  If $\Gamma \vdash {\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P$, then
  $\Gamma \vdash {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P$
\end{prop}

@@

\begin{defin} Monoidal functor

@@

  A monoidal functor $\mathcal{F} : \langle \mathcal{C}, \otimes_1, \mathds{1} \rangle \to \langle \mathcal{D}, \otimes_2, \mathds{1}' \rangle$ is a functor
  $\mathcal{F} : \mathcal{C} \to \mathcal{D}$ with additional natural transformations, which satisfy the well-known conditions described in \cite{ElKelly}:

@@

  An applicative functor is a triple $\langle \mathcal{C}, \mathcal{K}, \eta \rangle$,
where $\mathcal{C}$ is a symmetric monoidal category, $\mathcal{K}$ is a monoidal endofunctor and $\eta : Id_{\mathcal{C}} \Rightarrow \mathcal{K}$ is a natural transformation (similar to unit in monad), such that:

@@

@@

$[\![A \to B]\!] := [\![A]\!] \to [\![B]\!]$;

@@

@@

We will denote equivalence class as $[x, M]_{A, B} = \{ (y, N) \: | \: (x, M) \sim_{A, B} (y, N) \}$ (we will drop indeces below).

>>>>

Where $\mathbb{V}^{*}$ and $\Lambda_{{\bf K}}^{*}$ denote the set of finite sequences of variables $\bigcup \limits_{i=0}^{\infty} \mathbb{V}_i$
and the set of finite sequences of terms $\bigcup \limits_{i = 0}^{\infty} {\Lambda_{{\bf K}}}_i $. Note that the sequence of variables $\vec{x}$ and the sequence of terms $\vec{M}$ should have the same length.
Otherwise, term is not well-formed.

@@

@@

Also we accept the following equality, so called symmetricity of local binding:

\begin{defin} Symmetricity of local binding

  ${\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P \equiv {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P$

This commuting relation denotes that we identify terms of kind {\bf let pure} if they are differ in the order of binding.

@@

\begin{prop}

  If $\Gamma \vdash {\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P : {\bf K}A$, then
  $\Gamma \vdash {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P : {\bf K}A$.
\end{prop}

@@

\begin{defin} Lax monoidal functor

@@

  A lax monoidal functor $\mathcal{F} : \langle \mathcal{C}, \otimes_1, \mathds{1} \rangle \to \langle \mathcal{D}, \otimes_2, \mathds{1}' \rangle$ is a functor
  $\mathcal{F} : \mathcal{C} \to \mathcal{D}$ with additional natural transformations, which satisfy the well-known conditions described in \cite{ElKelly}:

@@

  An applicative functor is a triple $\langle \mathcal{C}, \mathcal{K}, \eta \rangle$,
where $\mathcal{C}$ is a symmetric monoidal category, $\mathcal{K}$ is a lax monoidal endofunctor and $\eta : Id_{\mathcal{C}} \Rightarrow \mathcal{K}$ is a natural transformation (similar to unit in monad), such that:

@@

By default we will consider a strong functor on cartesian closed category with $\eta$ \cite{Cons}.

@@

$[\![A \to B]\!] := [\![B]\!]^{[\![A]\!]}$;

@@

\begin{prop}
$ $

  $[\![\Gamma \vdash {\bf let \: pure \:} \vec{x}, \vec{y} = \vec{M}, \vec{N} {\: \bf in \:} P : {\bf K} C]\!] = [\![\Gamma \vdash {\bf let \: pure \:} \vec{y}, \vec{x} = \vec{N}, \vec{M} {\: \bf in \:} P : {\bf K} C]\!]$
\end{prop}

  Follows from the commutativity of the following diagram:

\xymatrix{
[\![\Gamma]\!] \ar[rr]^{\langle g, f \rangle} \ar[d]_{\langle f, g \rangle} && \mathcal{K}[\![B]\!] \times \mathcal{K}[\![A]\!] \ar[rr]^{\ast_{[\![B]\!], [\![A]\!]}}
\ar[d]_{\ast_{[\![A]\!], [\![B]\!]} \circ \langle \pi_2, \pi_1 \rangle} && \mathcal{K}([\![B]\!] \times [\![A\!]) \ar[d]^{\mathcal{K}{[\![N]\!]} \circ \mathcal{K}(\langle \pi_2, \pi_1 \rangle)} \\
\mathcal{K}[\![A\!] \times \mathcal{K}[\![B]\!] \ar[rr]_{\ast_{[\![A]\!], [\![B]\!]}} && \mathcal{K}([\![A]\!] \times [\![B]\!]) \ar[rr]_{[\![N]\!]}&& \mathcal{K}[\![C]\!]
}

@@

We will denote equivalence class as $[x, M]_{A, B} = \{ (y, N) \: | \: (x, M) \sim_{A, B} (y, N) \}$ (we will drop indices below).
